Management induced changes of soil organic carbon on global croplands

### 2020-08-14 ResultNotebooks/results_SOCcompare.Rmd
refine results scripts (specially flow figure)

rev <- "rev0.6_mrSOC"

@@

mipLineHistorical(reg_SOCStock, hist, facet.ncol=4, scales="free_y", ylab="SOC (0-30cm) in MtC")
```

@@

>>>>

rev       <- "rev0.6_mrSOC"
outputdir <- "Output/Images"

@@

regSOCcompare <- mipLineHistorical(reg_SOCStock, hist, facet.ncol=4, scales="free_y", ylab="SOC (0-30cm) in MtC")

ggsave(paste0(outputdir,"/4panelfigure.png"), plot=grid)
```

@@

```{r plot diff maps, out.width="100%", out.height=1000}

library(luplot)
library(magpiesets)

cellSOCdens   <- (dimSums(dimSums(SoilCarbon[,,"naturalstate"], dim=3.2) * Landuse, dim=c(3))/dimSums(Landuse, dim=c(3)))[,findset("past"),]
cellSOCdens[is.na(cellSOCdens)] <- 0

cellSoilGrids <- readSource("SoilGrids", subtype="cstock_0_30", convert="onlycorrect")
cellLPJml     <- calcOutput("LPJmL", version="LPJmL4", climatetype="CRU_4", subtype="soilc_layer", time="raw", selectyears="past", aggregate=FALSE)
cellLPJml     <- collapseNames(cellLPJml[,,"layer1"]+1/3*cellLPJml[,,"layer2"], collapsedim = c(2,3))

diffSoilGrids <- cellSOCdens - cellSoilGrids
diffLPJml     <- cellSOCdens - cellLPJml

luplot::plotmap(diffLPJml[,10,], legend_range = c(-80,80))
```

### 2020-08-14 ResultNotebooks/results_SOCflows.Rmd
refine results scripts (specially flow figure)

rev <- "rev0.6_mrSOC"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data", extras="--keep-newer-files ")

SoilCarbon <- read.magpie("Data/SoilCarbon.rds")
Landuse    <- read.magpie("Data/Landuse.rds")

@@

CarbonInput      <- readRDS("Data/CarbonInput.rds")
CarbonLitter     <- readRDS("Data/CarbonLitter.rds")
CarbonManure     <- readRDS("Data/CarbonManure.rds")           
CarbonResidues   <- readRDS("Data/CarbonResidues.rds")
CarbonHarvest    <- readRDS("Data/Crop_Harvest.rds")
SoilCarbon       <- readRDS("Data/SoilCarbon.rds")

@@

>>>>

rev       <- "rev0.7_mrSOC"
outputdir <- "Output/Images"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
#untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data", extras="--keep-newer-files ")

@@

CarbonInput      <- readRDS("Data/CarbonInput.rds")
CarbonLitter     <- readRDS("Data/CarbonLitter.rds")
CarbonManure     <- readRDS("Data/CarbonManure.rds")           
CarbonResidues   <- readRDS("Data/CarbonResidues.rds")
CarbonHarvest    <- readRDS("Data/Crop_Harvest.rds")
SoilCarbonOut    <- readRDS("Data/SoilCarbon.rds")
SoilCarbonDecay  <- readRDS("Data/SoilDecay.rds")
SoilCarbonStSt   <- readRDS("Data/SoilSteadyState.rds")

@@

```{r globals}
grepSpaceTime     <- function(x){return(dimSums(x[,"y2010","c"],dim=1))}

#Agriculture
kcr        <- findset("kcr")
kli        <- findset("kli")
kres       <- findset("kres")
kExResPast <- setdiff(findset("kall"),c(kres,kli,"pasture","wood","woodfuel","scp","fish"))
kPrim      <- setdiff(findset("kall"),c(kli,"scp","fish"))

CropHANPP         <- dimSums(grepSpaceTime(FAOmassbalance[,,kcr][,,c("food","waste","other_util","bioenergy","feed",
                                                                     "milling","refining","extracting","fermentation","distilling")]), dim=3)
CropFEED          <- grepSpaceTime(dimSums(FAOmassbalance[,,kExResPast][,,"feed"], dim=3.1))
CropPRIM          <- CropHANPP-CropFEED
ResFEED           <- grepSpaceTime(dimSums(FAOmassbalance[,,kres][,,"feed"], dim=3.1))
ResPRIM           <- dimSums(grepSpaceTime(FAOmassbalance[,,kres][,,c("other_util","bioenergy")]), dim=3)

FEED              <- grepSpaceTime(dimSums(FAOmassbalance[,,kPrim][,,"feed"], dim=3.1))
LivstHANPP        <- dimSums(grepSpaceTime(FAOmassbalance[,,kli][,,c("food","waste","other_util")]), dim=3)
LivstCropHANPP    <- (CropFEED+ResFEED)/FEED * LivstHANPP

ResidueBiomassTot <- grepSpaceTime(dimSums(ResidueBiomass, dim=3.2))
ResidueRecycledTot<- grepSpaceTime(dimSums(ResiduesAgDemand[,,"recycle"], dim=3.2))

ManureExcretedTot <- grepSpaceTime(dimSums(ManureExcreted[,,c("stubble_grazing","confinement")], dim=c(3.1,3.2)))
ManureRecycledTot <- grepSpaceTime(dimSums(ManureRecycled, dim=3.1))

#Soil

### Carbon To
CarbonTo            <- dimSums(toolConditionalReplace(SoilCarbonOut[,"y2010","carbontransfer"], "<0", 0),dim=c(1,3.3))
CarbonToEff         <- dimSums(SoilCarbonOut[,"y2010","carbontransfer"], dim=c(1,3.3))
CarbonToPools       <- dimSums(toolConditionalReplace(SoilCarbonOut[,"y2010","carbontransfer"], "<0", 0),dim=c(1))

####### delete when new output on decay is ready
# Decay

ActiveDecay        <- mbind(setNames(calcOutput("ActiveDecay",  landtype="crop",   aggregate = FALSE),"crop"),
                              setNames(calcOutput("ActiveDecay",  landtype="natveg", aggregate = FALSE),"natveg"))
SlowDecay          <- mbind(setNames(calcOutput("SlowDecay",  landtype="crop",   aggregate = FALSE),"crop"),
                              setNames(calcOutput("SlowDecay",  landtype="natveg", aggregate = FALSE),"natveg"))
PassiveDecay       <- mbind(setNames(calcOutput("PassiveDecay", landtype="crop",   aggregate = FALSE),"crop"),
                              setNames(calcOutput("PassiveDecay", landtype="natveg", aggregate = FALSE),"natveg"))

subpools     <- c("active","slow","passive")
names        <- as.vector(outer(getNames(Landuse), subpools, paste, sep="."))
Decay <- new.magpie(getCells(Landuse), getYears(Landuse), names, fill = 0)

Decay[,,"active"]                  <- ActiveDecay
Decay[,,"slow"]                    <- SlowDecay
Decay[,,"passive"]                 <- PassiveDecay

rm(ActiveDecay, SlowDecay, PassiveDecay)

#
####### end delete

DecayCut          <- Decay
DecayCut[Decay>1] <- 1

### Carbon In
f1        <- param[,,"f1"]
f2_crop   <- param[,,"f2_ft"]
f2_natveg <- param[,,"f2_nt"]
f3        <- param[,,"f3"]

# f2 has to be updated with new test runs

MineralizeFracInput <- setCells(mbind(add_dimension(collapseNames(CarbonInput[,,"totalC",invert=TRUE][1,,"res"]), dim=3.1, add = "lu", nm = "crop"),
                                      add_dimension(collapseNames(CarbonInput[,,"totalC",invert=TRUE][1,,"res"]), dim=3.1, add = "lu", nm = "natveg")), "GLO")
MineralizeFracInput[,,"metabDOC"]        <- f1
MineralizeFracInput[,,"crop.strucDOC"]   <- f2_crop
MineralizeFracInput[,,"natveg.strucDOC"] <- f2_natveg
MineralizeFracInput[,,"ligninC"]         <- f3

input2lu <- as.data.frame(list(c("res", findset("kli"), "litfall"),
                            c(rep("crop",6), "natveg")), col.names=c("input","lu"))

CarbonInEff       <- collapseNames(dimSums(toolAggregate(CarbonInput[,"y2010",][,,"totalC",invert=TRUE], rel=input2lu, dim=3.1) *
                                            MineralizeFracInput[,"y2010",] * Landuse[,"y2010",], dim=c(1,3.2)))

CarbonInSource   <- collapseNames(dimSums(CarbonInput[,"y2010",][,,"totalC",invert=TRUE]  * 
                                            toolAggregate(MineralizeFracInput[,"y2010",] * Landuse[,"y2010",], rel=input2lu, from="lu", to="input", dim=3.1), dim=c(1,3.2)))

CarbonInRaw       <- collapseNames(dimSums(SoilCarbonOut[,"y2010","steadystate"]*DecayCut[,"y2010",]*Landuse[,"y2010",], dim=c(1,3.3)))

### Carbon Out

CarbonOutRaw      <- collapseNames(dimSums(SoilCarbonOut[,"y2010","interstate"]*DecayCut[,"y2010",]*Landuse[,"y2010",], dim=c(1,3.3)))
CarbonOutEff      <- CarbonOutRaw + CarbonInEff - CarbonInRaw

### SOC State

SOCstate <- dimSums(SoilCarbonOut[,c("y2009","y2010"),c("actualstate","interstate")]*Landuse[,c("y2009","y2010"),], dim=c(1,3.3))

### 2020-08-14 ResultNotebooks/results_SOCmaps.Rmd
refine results scripts (specially flow figure)

rev <- "rev0.6_mrSOC"

@@

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(glo_SOCEmission)[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = "Global cummulative SOC emission in GtC") +
  scale_x_discrete(breaks=seq(1965,2010,5)) +
  scale_y_continuous(limits=c(25,40), breaks=seq(25,40,5)) +
  theme(rect=element_blank())

@@

library("ggplot2")
theme_set(theme_bw())
library("sf")
library("rnaturalearth")
library("rnaturalearthdata")
library(RColorBrewer)

cols_dens <- colorRampPalette(brewer.pal(11, "RdYlBu"))(30)[c(1:20, rep(c(21:30), each=10))]

outputdir <- "Output/Images"

world         <- ne_countries(scale = "medium", returnclass = "sf")
magpie_coord  <- toolGetMapping("magpie_coord.rda", type="cell")
share2plot    <- merge(as.data.frame(cropland_share), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")
increase2plot <- merge(as.data.frame(cropland_increase), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")
density2plot  <- merge(as.data.frame(cropland_dens), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")
cols          <- colorRampPalette(brewer.pal(11, "RdYlBu"))(7)
world.robin   <- st_transform(world,"+proj=robin +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs")

SOCshare <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(share2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(0,2), colours = cols, 
                      name = expression("ratio of cropland SOC to potential natural SOC"), 
                      breaks=c(0.3,0.6,0.9,1.1,1.4,1.7,2),
                      labels=c("0     0.3","  0.6", "  0.9","  1.1","  1.4","  1.7","> 2"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=10),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = T,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7))
          )

SOCincrease <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(increase2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(-100,100), colours = cols, 
                      name = expression("cropland SOC change in tons of carbon per hectar"), 
                      values=(c(-100,-50,-20,-10,10,20,50,100)+100)/200,
                      breaks=c(-50,-20,-10,10,20,50,100),
                      labels=c("> -100    -50", "  -20","  -10","  10","  20","  50"," > 100"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=10),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = T,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7))
          )

cols <- colorRampPalette(brewer.pal(9, "YlGn"))(8)[2:8]
display.brewer.pal(9, "YlGn")
display.brewer.pal(9, "RdYlGn")

SOCdensity <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(density2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(0,150), colours = cols, 
                      name = expression("cropland SOC in tons of carbon per hectar"), 
                      values=c(0,5,10,20,40,70,100,150)/150,
                      breaks=c(5,10,20,40,70,100,150),
                      labels=c("0     5","  10","  20","  40","  70","  100"," >150"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=10),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = T,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7))
          )

@@

```{r grid plot}
library(gridExtra)

grid <- grid.arrange(SOCdensity, SOCemis, SOCincrease, SOCshare, ncol=2)
grid
ggsave(paste0(outputdir,"/4panelfigure.png"), plot=grid)

@@

```{r plot diff maps, out.width="100%", out.height=1000}

library(luplot)
library(magpiesets)

cellSOCdens   <- (dimSums(dimSums(SoilCarbon[,,"naturalstate"], dim=3.2) * Landuse, dim=c(3))/dimSums(Landuse, dim=c(3)))[,findset("past"),]
cellSOCdens[is.na(cellSOCdens)] <- 0

cellSoilGrids <- readSource("SoilGrids", subtype="cstock_0_30", convert="onlycorrect")
cellLPJml     <- calcOutput("LPJmL", version="LPJmL4", climatetype="CRU_4", subtype="soilc_layer", time="raw", selectyears="past", aggregate=FALSE)
cellLPJml     <- collapseNames(cellLPJml[,,"layer1"]+1/3*cellLPJml[,,"layer2"], collapsedim = c(2,3))

diffSoilGrids <- cellSOCdens - cellSoilGrids
diffLPJml     <- cellSOCdens - cellLPJml

luplot::plotmap(diffLPJml[,10,], legend_range = c(-80,80))
```

```{r plot density maps 2}

cols <- colorRampPalette(brewer.pal(9,"Oranges"))(1000)
cropland <- dimSums(SoilCarbon[,,"crop"], dim=3)
cropland[Landuse[,,"crop"]==0] <- NA

luplot::plotmap(cropland[,"y2010",], legend_colours = cols, legend_range=range(cropland[,"y2010",]/5, na.rm=TRUE))

natland <- dimSums(SoilCarbon[,,"natveg"], dim=3)

luplot::plotmap(natland[,"y2010",], legend_colours = cols, legend_range=range(cropland[,"y2010",]/5, na.rm=TRUE))

>>>>

rev       <- "rev0.7_mrSOC"
outputdir <- "Output/Images"

@@

library(ggplot2)

@@

@@

magpie_coord  <- toolGetMapping("magpie_coord.rda", type="cell")
share2plot    <- merge(as.data.frame(cropland_share), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")
increase2plot <- merge(as.data.frame(cropland_increase), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")
density2plot  <- merge(as.data.frame(cropland_dens), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")

@@

```{r grid plot}

library("ggplot2")
theme_set(theme_bw())
library("sf")
library("rnaturalearth")
library("rnaturalearthdata")
library(RColorBrewer)
library(sp)
library(rworldmap)
library(oce)

legend_size <- 10

map.world <- map_data("world")
world         <- ne_countries(scale = "medium", returnclass = "sf")
data(coastlineWorld)  
coastline.world <- data.frame(longitude=coastlineWorld[["longitude"]],latitude=coastlineWorld[["latitude"]])

SOCemis <- ggplot() + geom_line(data= as.data.frame(glo_SOCEmission[,seq(1975,2010,5),])[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = "Global cummulative \nSOC emission in GtC") +
  scale_x_discrete(breaks=seq(1965,2010,5)) +
  scale_y_continuous(limits=c(30,40), breaks=seq(30,40,5)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8))

cols          <- colorRampPalette(brewer.pal(11, "RdYlBu"))(7)

SOCshare <- ggplot(data = world) + geom_sf() + 
    geom_tile(data = subset(share2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(0,2), colours = cols, 
                      name = expression("ratio of cropland SOC to potential natural SOC"), 
                      breaks=c(0.3,0.6,0.9,1.1,1.4,1.7,2),
                      labels=c("0     0.3","  0.6", "  0.9","  1.1","  1.4","  1.7","> 2"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7))
          )

#geom_map(dat=map.world, map = map.world, aes(map_id=region), fill="NA", color="black") +

SOCincrease <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(increase2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(-100,100), colours = cols, 
                      name = expression("cropland SOC change in tons of carbon per hectar"), 
                      values=(c(-100,-50,-20,-10,10,20,50,100)+100)/200,
                      breaks=c(-50,-20,-10,10,20,50,100),
                      labels=c("> -100    -50", "  -20","  -10","  10","  20","  50"," > 100"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7))
          )

cols <- colorRampPalette(brewer.pal(9, "YlGn"))(8)[2:8]

SOCdensity <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(density2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(0,150), colours = cols, 
                      name = expression("cropland SOC in tons of carbon per hectar"), 
                      values=c(0,5,10,20,40,70,100,150)/150,
                      breaks=c(5,10,20,40,70,100,150),
                      labels=c("0     5","  10","  20","  40","  70","  100"," >150"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7))
          )

library(gridExtra)
library(cowplot)
grid <- plot_grid(SOCdensity, SOCemis, SOCincrease, SOCshare, ncol=2, labels=c("a","b", "c", "d"),
                  label_fontface = "plain", label_size = 10)
grid
ggsave(paste0(outputdir,"/4panelfigure.png"), plot=grid)

@@

### 2020-08-14 ResultNotebooks/results_SOCtable.Rmd
update results
refine results scripts (specially flow figure)

rev <- "rev0.6_mrSOC"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data", extras="--keep-newer-files ")

@@

@@

saveRDS(list(naturalstate_table = naturalstate_table,
             actualstate_table  = actualstate_table, 
             steadystate_table  = steadystate_table), "Output/SFC_climatezone.rds")

@@

comparison <- mbind(CShare_ipcc, 
                    round(add_dimension(collapseNames(CShare_ipcczone[,"y2010","naturalstate"]),
                                  add="SOCbudget",nm="model"),2))

@@

@@

>>>>

rev       <- "rev0.7_mrSOC"
outputdir <- "Output/"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
#untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data", extras="--keep-newer-files ")

@@

getNames(CShare_ipcczone) <- gsub("_", " ", getNames(CShare_ipcczone))

@@

saveRDS(list(naturalstate_table = naturalstate_table,
             actualstate_table  = actualstate_table, 
             steadystate_table  = steadystate_table), paste0(outputdir, "SFC_climatezone.rds"))

@@

getNames(CShare_ipcc) <- gsub("_", " ", getNames(CShare_ipcc))

comparison <- mbind(CShare_ipcc, 
                    round(add_dimension(setYears(collapseNames(CShare_ipcczone[,"y1990","naturalstate"]),"y2010"),
                                  nm="SOCbudget 1990",add="model"),2),
                    round(add_dimension(collapseNames(CShare_ipcczone[,"y2010","naturalstate"]),
                                  nm="SOCbudget 2010",add="model"),2))

@@

comparison_table  <- data.frame(dcast(as.data.frame(collapseNames(comparison)), 
                            Data1 ~ Data2, value.var="Value", 
                            row.names=levels(as.data.frame(comparison)$Data1)))

saveRDS(list(comparison_table = comparison_table), paste0(outputdir,"SFC_comparison.rds"))

@@

```{r kable2image}
library(kableExtra)

table <- readRDS("Output/SFC_comparison.rds")
colnames(table[[1]]) <- gsub("_", " ", colnames(table[[1]]))
colnames(table[[1]])[1] <- "Source"
save_kable(kable_styling(kable(table$comparison_table, "latex", digit=2), latex_options = c("striped", "scale_down")), 
         file="Output/Images/TableSCF_comparison.png")

table <- readRDS("Output/SFC_climatezone.rds")
colnames(table[[1]]) <- gsub("_", " ", colnames(table[[1]]))
colnames(table[[1]][1]) <- ""
as_image(kable_styling(kable(table$naturalstate_table[3:10,], "latex", digit=2), latex_options = c("striped", "scale_down")), 
         width=4, file="Output/Images/TableSCF_timeline.png")
```

### 2020-08-14 SOCbudgetPaper/SOCbudget.Rmd
refine results scripts (specially flow figure)

journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'communication')`"
author:
  - given_name: Kristine
    surname: Karstens
    affiliation: 1
    email: kristine.karstens@pik-potsdam.de
    corresponding: true
  - given_name: Benjamin Leon
    surname: Bodirsky
    affiliation: 1
  - given_name: Your
    surname: Name
    affiliation: 2
  - given_name: Alexander
    surname: Popp
    affiliation: 1
affiliation:
  - code: 1
    address: Potsdam-Institut of Climate Impacts Research, Potsdam, Germany
  - code: 2
    address: Your affiliation 
abstract: | 
  Soil organic carbon (SOC) is one of larges c stocks on earth (3 times larger biosphere pool). 
bibliography: SOCbudget.bib
running:
  title: R Markdown Template for Copernicus
  author: Nüst et al.
competinginterests: |
  The authors declare no competing interests.
# OPTIONAL:
algorithms: true
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed.
copyrightstatement: |
  The author's copyright for this publication is transferred to institution/company.
availability:
  codedata: |
    use this to add a statement when having data sets and software code available
authorcontribution: |
  Karstens wrote code and paper build on work of Bodirsky. Bodirsky, <here_could_be_your_names> and Popp revised paper.
disclaimer: |
  We like Copernicus.
acknowledgements: |
  Thanks to the rticles contributors!
appendix: |
  \section{Figures and tables in appendices}
  \subsection{Option 1}
  If you sorted all figures and tables into the sections of the text, please also sort the appendix figures and appendix tables into the respective appendix sections.
  They will be correctly named automatically.
  \subsection{Option 2}
  If you put all figures after the reference list, please insert appendix tables and figures after the normal tables and figures.

  `\appendixfigures` needs to be added in front of appendix figures
  `\appendixtables` needs to be added in front of appendix tables

  Please add `\clearpage` between each table and/or figure. Further guidelines on figures and tables can be found below.
  Regarding figures and tables in appendices, the following two options are possible depending on your general handling of figures and tables in the manuscript environment:
  To rename them correctly to A1, A2, etc., please add the following commands in front of them:
output:
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
    md_extensions: +raw_attribute
  md_document:
    variant: markdown_github
  bookdown::word_document2: default
  bookdown::pdf_document2: default
  rticles::copernicus_article: default
---
\newpage

@@

>>>>

journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'communication')`"
author:
  - given_name: Kristine
    surname: Karstens
    affiliation: 1
    email: kristine.karstens@pik-potsdam.de
    corresponding: true
  - given_name: Benjamin Leon
    surname: Bodirsky
    affiliation: 1
  - given_name: Your
    surname: Name
    affiliation: 2
  - given_name: Alexander
    surname: Popp
    affiliation: 1
affiliation:
  - code: 1
    address: Potsdam-Institut of Climate Impacts Research, Potsdam, Germany
  - code: 2
    address: Your affiliation 
abstract: |
  Soil organic carbon (SOC) is one of larges carbon stocks on earth. It is three times larger than the biospheric pool and more than twice as big as the athmospheric pool, when looking into the first meter of the earth soil profile. Human cropping activties led and still lead to a depletion of SOC though, which are so far not well represented in global assessments of historic carbon emissions. While SOC models often represent well the biochemical processes that lead to the accumulation and decay of SOC, the management decisions driving these biophysical processes are still little investigated on the global scale. 
 Here we create a spatial explicit data set for agricutural management on cropland, especially for crop residue and manure management, based on global historic production (FAOSTAT), and land-use (LUH2) data; and combine it with the IPCC Tier 2 approach to create a half degree resolution SOC stock changes on mineral soils. We estimate that due to arable farming soils have lost over (?) GtOC of which (??) GtOC have been regained within the period 1975-2010. 
 We show that, our results on global scale based on Tier 2 IPCC methodolgy are in good agreement with Tier 1 default assumptions. We also find that SOC is very sensitive to management decision such as residue recycling indicating the nessessity to incorporated better management data in soil models.
bibliography: SOCbudget.bib
running:
  title: R Markdown Template for Copernicus
  author: Nüst et al.
competinginterests: |
  The authors declare no competing interests.
# OPTIONAL:
algorithms: true
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed.
copyrightstatement: |
  The author's copyright for this publication is transferred to institution/company.
availability:
  codedata: |
    Software code for paper and result prepartion can be found under www.github.com/k4rst3ns/. Data used for the output can be found under <something-with-zenodo>.  
authorcontribution: |
  Karstens wrote code and paper build on work of Bodirsky (and <here_could_be_your_names>). 
  Bodirsky, <here_could_be_your_names> and Popp revised paper.
disclaimer: |
  We like Copernicus.
acknowledgements: |
  Thanks to the rticles contributors!
output:
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
    md_extensions: +raw_attribute
  md_document:
    variant: markdown_github
  bookdown::word_document2: default
  bookdown::pdf_document2: default
  rticles::copernicus_article: default
---
\newpage

@@

```{r child = 'appendix.Rmd'}
```
\newpage
